### 2020-08-27 Thesis-Chapter2-Background.tex
Additional reading. 'Wicked Crypto' is an excellent source
Several build updates; add arguments
Update to Node 12.x; add 'fallacies' argument map

% TODO: Review recent cases. See orenstein_2016, bittenbender_2019, vaas_2019.

@@

The \ac{SAFEAct} would have broadly protected ``use any encryption regardless of the encryption algorithm selected,
encryption key length chosen, or implementation technique or medium used,'' excepting ``the unlawful use of encryption
in furtherance of a criminal act.'' It also would have lifted export controls. The bill grew support as it was
reintroduced in consecutive congresses, but was abandoned when the Clinton administration adopted the act's
pro-encryption policies in 1999 \cite{:kehl_right_2015}.

@@

>>>>

% TODO: Review recent cases. See orenstein_2016, bittenbender_2019, vaas_2019.
% NOTE: _Carpenter_ was a recent important Supreme Court case limiting the scope of the third-party doctrine!
% See franklin_2018 and rozenshtein_2018

@@

The \ac{SAFEAct} would have broadly protected ``use any encryption regardless of the encryption algorithm selected,
encryption key length chosen, or implementation technique or medium used,'' excepting ``the unlawful use of encryption
in furtherance of a criminal act.'' It also would have lifted export controls. The bill grew support as it was
reintroduced in consecutive congresses, but was abandoned when the Clinton administration adopted the act's
pro-encryption policies in 1999 \cite{kehl_right_2015}.

@@

% TODO: add wright_crypto_2018 (I _think_ it goes here)

\propsend

### 2020-08-27 Thesis-Chapter3-Arguments.tex
Several build updates; add arguments
Update to Node 12.x; add 'fallacies' argument map

In this chapter, develop the arguments employed in EA debates. Make use of argument maps to break down and visualize the
debate, as shown in \myfig{fig-args-top-level}.

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=\linewidth]{arguments/build/top-level.pdf}
    \caption[Argument: Top Level]{Top level arguments for and against exceptional access.}
    \label{fig-args-top-level}
\end{figure}

@@

>>>>

% In this chapter, develop the arguments employed in EA debates. Make use of argument maps to break down and visualize the
% debate, as shown in \myfig{fig-args-top-level}.

% \begin{figure}[h]
%     \centering\CaptionFontSize
%     \includegraphics[width=\linewidth]{arguments/build/top-level.pdf}
%     \caption[Argument: Top Level]{Top level arguments for and against exceptional access.}
%     \label{fig-args-top-level}
% \end{figure}

@@

\subsection{Fallacious Arguments}

Fallacy definitions come from the helpful University of North Carolina Writing Center \cite{unc_2020}.
